Body Image and Trikafta

### 2023-03-24 Emily Muther/body_image_trikafta.qmd
Update body_image_trikafta.qmd
Latex not working for some reason

---
title: "Body Image and Trikafta"
author: "Tim Vigers"
date: today
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: visual
---

```{python}
# | include: false
import pandas as pd
# Read in data
df = pd.read_spss(
    "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Body Image and Trikafta/Data_Raw/TrikaftaBodyImage3.6.23.sav")
```

@@

```{python}
# | include: false
# | eval: false
from ydata_profiling import ProfileReport
# EDA
profile = ProfileReport(df, explorative=True)
# Saving results to a HTML file
profile.to_file(
    "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Body Image and Trikafta/Reports/eda.html")
```

```{python}
# Filter
df = df[df["TakingTrikafta"] == "yes"]
```

```{python}
# | label: tbl-planets
# | tbl-cap: Planets

@@

```{python}
# | label: fig-planets
# | fig-cap: Planets

>>>>

---
title: "Body Image and Trikafta"
author: "Tim Vigers"
date: today
date-format: long
format:
  pdf:
    toc: true
    toc-depth: 5
    lot: true
    lof: true
execute:
  echo: false
pdf-engine: pdflatex
editor: source
---

@@

```{r warning=FALSE}
#| include: false
library(tidyverse)
library(gtsummary)
library(kableExtra)
library(foreign)
# Read in data
df = read.spss("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Emily Muther/Body Image and Trikafta/Data_Raw/TrikaftaBodyImage3.6.23.sav",to.data.frame = T)
# Filter
df = df %>% 
  filter(TakingTrikafta=="yes")
# Pick relevant columns
df = df %>% 
  select(ID,Age,Gender,PercentAdherence,DosesMissed,FeelTrikafta,
         DifferencesTrikafta,BMI,FEV1,Race,Ethnicity,InsuranceType,
         WeightBody_Adherence,DoNotWantTrikafta,ContinueTrikafta,
         FRS_Category,contains("BE_"),contains("PHQ9"),contains("GAD7"),
         -contains("MEAN"))
```

# Descriptive analyses

```{r}
#| label: tbl-1
#| tbl-cap: Baseline characteristics by FRS category
#| message: false
df %>% select(-ID) %>%
  tbl_summary(by = FRS_Category) %>%
  as_kable_extra(
    booktabs = TRUE,
    longtable = TRUE
  ) %>% 
  kable_styling(
    full_width = T,
    latex_options = "repeat_header"
  )
```

```{r}
# | label: fig-planets
# | fig-cap: Planets

@@
